Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Conclusion, acknowledgements
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

\section{Discussion} \label{Sec:Impacts}

\textbf{TODO} - Recap impacts on real-world systems like MD5, SHA-1, etc.

@@

\textbf{TODO: COMPLETE}

@@

The authors would like to thank the Department of Electrical and Computer
Engineering and XXXXX XXXXX for providing hardware.

>>>>

@@

- Theory behind Logical Cryptanalysis:
    - Distance heuristic.
    - $\precsim$.
- Tie into Trustworthiness of hash functions.
- Demonstrated metrics.
- Demonstrated 35k new collisions.
- Implications to real world systems.

@@

The authors would like to thank XXXXX XXXXX for providing hardware for the
project.
